Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-15 Paper/paper.tex
Re wording use of robust

Note that the classic definition of PoA has been modified here to allow for a maximisation problem.
Social welfare is here considered to be a maximisation of throughput.
An immediate alignment of interests can be obtained by setting $t=1$.
This however would not be in the interest of the hospital (nor necessarily in the interests of patients) as it would imply aiming to run at 100\% utilisation which would not make for a robust system.
\textbf{A sensible value of $t$ is the lowest value of $t$ that ensures a low PoA}.

>>>>

Note that the classic definition of PoA has been modified here to allow for a maximisation problem.
Social welfare is here considered to be a maximisation of throughput.
An immediate alignment of interests can be obtained by setting $t=1$.
This however would not be in the interest of the hospital (nor necessarily in the interests of patients) as it would imply aiming to run at 100\% utilisation which imply a large quantity of patients being rejected.
\textbf{A sensible value of $t$ is the lowest value of $t$ that ensures a low PoA}.
